---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) package 
that provides function for binomial distribution.

* `bin_choose()` allows you to calulate the number of combinations
* `toss()` tosses a coin object, producing a `"toss"` object.
* `plot()` method for a `"toss"` object to plot frequencies of heads.
* `summary()` method for a `"toss"` object.


## Motivation

This package is created to help people calculate values in binomial distribution

## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("Kenan-Jiang/binomial")
# install "binomia" (with vignettes)
devtools::install_github("Kenan-Jiang/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(cointoss)
# default coin
coin1 <- coin()
coin1
# 1 toss of coin1
toss(coin1)
# 10 tosses of coin1
toss10 <- toss(coin1, times = 10)
toss10
# summary
summary(toss10)
# 100 tosses
toss100 <- toss(coin1, times = 100)
# summary
summary(toss100)
```